Recpature distances

### 2024-07-12 recaptureanalysis/recaps.Rmd
Cleaned up recapture analysis and biofouling bug analysis

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
library(tidyverse)
library(readxl)
library(sf)
library(lubridate)
library(spacetools)
library(deltamapr)
#load("Recaps.RData")
#save(nndist, distances, recaps, recaps2, recaps3, RVhdist, SCsoft, SChard, RVhdistx, Dwschard, Dwscsoft, file = "Recaps.RData")
```

@@

recaps3 = left_join(recaps2, distances) %>%
  mutate(Type2 = case_when(Type %in% c("Hard (large scale)","Hard (trailer)") ~ "Hard (Large Scale)",
                           TRUE ~ Type)) %>%
  mutate(SiteType = paste(Type, Site))

@@

write.csv(recaps, "recaptureanalysis/Recapturedistances.csv")
```

@@

distances = list(NA)

releasex = filter(release, ReleaseEvent %in% unique(recaps3$ReleaseEvent))
for(i in 1:nrow(releasex)) {
  points = filter(recaps3, ReleaseEvent == releasex$ReleaseEvent[i])
  distances[[i]] = Waterdist(Water_map = spacetools::Delta, Points = points, Latitude_column = `Latitude`,
                    Longitude_column = `Longitude`, PointID_column = FishID)
  names(distances[[i]]) = releasex$ReleaseEvent[i]

@@

clustest = lapply(distances, function(x){df = data.frame(Mean = mean(x[lower.tri(x)], na.rm =T), SD = sd(x, na.rm =T))} )%>%
  bind_rows() %>%
  mutate(Release = releasex$ReleaseEvent)

@@

alldist = lapply(distances, function(x){
  x[lower.tri(x, diag = T)] = NA
  X = as.data.frame(x) %>%
    mutate(Fish1 = row.names(x)) %>%
    pivot_longer(cols = -Fish1, names_to = "Fish2", values_to = "Distance") %>%
  filter(!is.na(Distance))
  return(X)
})

@@

@@

@@

ggplot(filter(releasestat, BroodYear != 2021, Type2 != "NA"), aes(x = weekturb, y = RecapRate )) + geom_point(aes(color = as.factor(BroodYear), shape = Type2), size =3)+ geom_smooth(method = "lm")+ylab("Percentage Recaptured") + 
  xlab("Mean turbidity for 7 days post release (NTU)")+
  theme_bw()+
  scale_color_brewer(palette = "Set2", name = "Brood Year")+
  scale_shape(name = "Release Type")

@@

>>>>

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
library(tidyverse)
library(readxl)
library(sf)
library(lubridate)
library(spacetools)
library(deltamapr)
load("Recaps2.RData")
save( distances, recaps, recaps2, recaps3,  distances2, alldist, alldist2, alldist2.1, releasestat,
      turbdat_ave, file = "Recaps2.RData")
```

@@

recaps3 = left_join(recaps2, distances, by = c("FishID" = "FishID")) %>%
  mutate(Type2 = case_when(Type %in% c("Hard (large scale)","Hard (trailer)") ~ "Hard (Large Scale)",
                           TRUE ~ Type)) %>%
  mutate(SiteType = paste(Type, Site))

@@

write.csv(recaps3, "recaptureanalysis/Recapturedistances.csv")
```

@@

distances2 = list(NA)

releasex = filter(release, ReleaseEvent %in% unique(recaps3$ReleaseEvent))
for(i in 1:nrow(releasex)) {
  points = filter(recaps3, ReleaseEvent == releasex$ReleaseEvent[i])
  distances2[[i]] = Waterdist(Water_map = spacetools::Delta, Points = points, Latitude_column = `Latitude`,
                    Longitude_column = `Longitude`, PointID_column = FishID)
  names(distances2[[i]]) = releasex$ReleaseEvent[i]

@@

clustest = lapply(distances2, function(x){df = data.frame(Mean = mean(x[lower.tri(x)], na.rm =T), SD = sd(x, na.rm =T))} )%>%
  bind_rows() %>%
  mutate(Release = releasex$ReleaseEvent)

@@

alldist = lapply(distances2, function(x){
  x[lower.tri(x, diag = T)] = NA
  X = as.data.frame(x) %>%
    mutate(Fish1 = row.names(x)) %>%
    pivot_longer(cols = -Fish1, names_to = "Fish2", values_to = "Distance") %>%
  filter(!is.na(Distance))
  return(X)
})

@@

alldist2 = mutate(alldist2, Type2 = case_when(str_detect(Type, "Hard") ~ "Hard",
                                              str_detect(Type, "Soft") ~ "Soft",
                                               TRUE ~ "Unknown"))
m22 = lm(Distance ~ Type2, data = filter(alldist2, Type != "Unknown"))
summary(m22)
plot(m22)

emmeans(m22, pairwise ~ Type2)
plot(emmeans(m22, pairwise ~ Type2), comparisons = T)

@@

But let's start with looking at just the paired releases with the carboys

```{r}
alldist3 = filter(alldist2, Type != "Unknown") %>%
  mutate(Pair = str_sub(ReleaseEvent, 1,8))
library(lme4)
library(lmerTest)

m3 = lmer(Distance ~ Type2 + (1|Pair), data = alldist3)
summary(m3)
plot(m22)

emmeans(m3, pairwise ~ Type2)
plot(emmeans(m3, pairwise ~ Type2), comparisons = T)

@@

turbm = lm(RecapRate ~ weekturb + Type2, data = releasestat)
summary(turbm)
#Huh, so percentage recaptures is correlated to turbidity (marginal), but not release type. Distance is correlated to release type, but not turbidity.

#what if i just use the paired hard/soft releases?
#oh, but some of the pairs are trailer and some are carboy

#Ugh, I need to talk throught this with Brian. 
write.csv(releasestat, "outputs/ReleasesRecapRate.csv")

```{r}
ggplot(filter(releasestat, BroodYear != 2021, Type2 != "NA"), aes(x = weekturb, y = RecapRate )) + geom_point(aes(color = as.factor(BroodYear), shape = Type2), size =3)+ geom_smooth(method = "lm")+ylab("Percentage Recaptured") + 
  xlab("Mean turbidity for 7 days post release (NTU)")+
  theme_bw()+
  scale_color_brewer(palette = "Set2", name = "Brood Year")+
  scale_shape(name = "Release Type")

@@

OK, now let's try adding turbidity to the model with the paired releases

alldist3 = left_join(alldist3, turbdat_ave, by = c("ReleaseDate" = "Date"))

m3.3 = lmer(Distance ~ Type2 +weekturb+ (1|Pair), data = alldist3)
summary(m3.3)

#hm. Turbidity isn't significant, but probably becaues i've already blocked by date of release

m3.4 = lm(Distance ~ Type2 +weekturb, data = alldist3)
summary(m3.4)
#turbidity is only marginal there.

alldist2 = left_join(alldist2, turbdat_ave, by = c("ReleaseDate" = "Date"))

m2.4 = lm(Distance ~ Type +weekturb, data = alldist2)
summary(m2.4)
#huh, turbidity not at all significant there.
